Characterizing Water Composition with an Autonomous Robotic Team Employing Comprehensive In-Situ Sensing, Hyperspectral Imaging, Machine Learning, and Conformal Prediction

### 2024-03-05 paper/paper.tex
Updates from Overleaf

\begin{figure}[t!]
\centering
\includegraphics[width=\columnwidth]{paper/figures/materials-and-methods/study-area.pdf}
\caption{The pond in Montague Texas where the robot team was deployed. The pond includes multiple distinct regions separated by small islands and grasses. \label{fig:study-area}}
\end{figure}

@@

\begin{figure}[h!]
\includegraphics[width=0.7\columnwidth]{paper/figures/results/downwelling-hist.pdf}
\caption{Distribution of total downwelling intensity during each of the three HSI collection flights. The multi-modal nature of these distributions reflects the impact of the relative orientation of the drone to the sun as well as potential occlusion due to the presence of clouds.\label{fig:downwelling-hist}}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=0.9\columnwidth]{paper/figures/results/fits/physical-fitres.png}
\caption{Scatter diagrams (left) and quantile-quantile plots (right) for the hyperparameter optimized RFR models for the physical variables measured by the USV.\label{fig:physical-fit}}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=\columnwidth]{paper/figures/results/fits/physical-ranking.pdf}
\caption{Ranked permutation importance for each feature in the physical variable models. Permutation importance measured the decrease in model $R^2$ value after replacing each feature in the prediction set with a random permutation of its values.\label{fig:physical-fi}}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=0.9\columnwidth]{paper/figures/results/maps/physical.pdf}
\caption{Maps generated by applying each of the physical variable models to the hyperspectral data cubes collected on 11-23. Overlaid over the predictions are color-filled squares showing the associated in-situ reference data for the same collection period. The size of the squares has been exaggerated for the visualization. We note that there is good agreement between the model predictions and the reference data. \label{fig:map-physical}}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{paper/figures/results/fits/ions-fitres.png}
\caption{Scatter diagrams (left) and quantile-quantile plots (right) for the hyperparameter optimized RFR models for the ion measurements made by the USV.\label{fig:ions-fit}}
\end{figure}

\begin{figure}
\begin{adjustwidth}{-\extralength}{0cm}
\centering
\includegraphics[width=18 cm]{paper/figures/results/fits/ions-ranking.pdf}
\end{adjustwidth}
\caption{Ranked permutation importance for the top 25 features of the ion models. The permutation importance measures the decrease in model $R^2$ value when each feature is replaced by a random permutation of its values.\label{fig:ions-fi}}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{paper/figures/results/maps/ions.pdf}
\caption{Maps generated by applying the trained ion models to the data cubes collected on 11-23. Overlaid on the maps are the in-situ reference measurements for the same collection period. The size of the squares has been exaggerated for the visualization. We note that there is good agreement between the generated map and the reference data. \label{fig:map-ions}}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{paper/figures/results/fits/biochemical-fitres.png}
\caption{Scatter plots (left) and quantile-quantile plots (right) for the final hyperparameter optimized models for the biochemical targets blue-green algae (phycoerythrin), CDOM, chlorophyll-a, and blue-green algae (phycocyanin). \label{fig:biochem-fit}}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{paper/figures/results/fits/biochemical-ranking.pdf}
\caption{Ranked permutation importance for each feature in the trained biochemical models. The permutation importance measures the decrease in model $R^2$ value after replacing each feature with a random permutation of its values.\label{fig:biochem-fi}}
\end{figure}

\begin{figure}
\centering
\vspace{-0.3in}
\includegraphics[width=\columnwidth]{paper/figures/results/maps/biochemical.pdf}
\vspace{-0.2in}
\caption{Maps generated by applying the trained biochemical models to the data cubes collected on 11-23. Overlaid are the in-situ reference data for the same collection period. The size of the squares has been exaggerated for the visualization. We note there is good agreement between the predicted map and the reference data. \label{fig:map-biochem}}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{paper/figures/results/fits/chemical-fitres.png}
\caption{Scatter diagrams (left) and quantile-quantile plots (right) for the hyperparameter optimized RFR models for the chemical variables measured by the USV.\label{fig:chemicals-fit}}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{paper/figures/results/fits/chemical-ranking.pdf}
\caption{Ranked permutation importance for for the top 25 features of the chemical models. The permutation importance measures the deacrease in model $R^2$ value after replacing each feature in the prediction set with a random permutation of its values.\label{fig:chemicals-fi}}
\end{figure}

\begin{figure}
\centering
\vspace{-0.3in}
\includegraphics[width=\columnwidth]{paper/figures/results/maps/chemical.pdf}
\caption{Maps generated by applying the trained chemical variable models to the hyperspectral data cubes collected on 11-23. Overlaid are color-filled squares showing the in-situ reference data for the same collection period. The size of the squares is exaggerated for the visualization. We note that there is good agreement between the model predictions and reference data.\label{fig:map-chem}}
\end{figure}

>>>>

\begin{figure}[t!]
\centering
\vspace{-0.3in}
\includegraphics[width=\columnwidth]{paper/figures/materials-and-methods/study-area.pdf}
\vspace{-0.3in}
\caption{The pond in Montague Texas where the robot team was deployed. The pond includes multiple distinct regions separated by small islands and grasses. \label{fig:study-area}}
\end{figure}

@@

\begin{figure}[t!]
\vspace{-0.3in}
\includegraphics[width=0.7\columnwidth]{paper/figures/results/downwelling-hist.pdf}
\vspace{-0.15in}
\caption{Distribution of total downwelling intensity during each of the three HSI collection flights. The multi-modal nature of these distributions reflects the impact of the relative orientation of the drone to the sun as well as potential occlusion due to the presence of clouds.\label{fig:downwelling-hist}}
\end{figure}

@@

\begin{figure}[t!]
\centering
\vspace{-0.3in}
\includegraphics[width=0.9\columnwidth]{paper/figures/results/fits/physical-fitres.png}
\vspace{-0.2in}
\caption{Scatter diagrams (left) and quantile-quantile plots (right) for the hyperparameter optimized RFR models for the physical variables measured by the USV.\label{fig:physical-fit}}
\end{figure}

@@

\begin{figure}[t!]
\centering
\vspace{-0.3in}
\includegraphics[width=\columnwidth]{paper/figures/results/fits/physical-ranking.pdf}
\vspace{-0.2in}
\caption{Ranked permutation importance for each feature in the physical variable models. Permutation importance measured the decrease in model $R^2$ value after replacing each feature in the prediction set with a random permutation of its values.\label{fig:physical-fi}}
\end{figure}

\begin{figure}[t!]
\centering
\vspace{-0.3in}
\includegraphics[width=0.9\columnwidth]{paper/figures/results/maps/physical.pdf}
\vspace{-0.2in}
\caption{Maps generated by applying each of the physical variable models to the hyperspectral data cubes collected on 11-23. Overlaid over the predictions are color-filled squares showing the associated in-situ reference data for the same collection period. The size of the squares has been exaggerated for the visualization. We note that there is good agreement between the model predictions and the reference data. \label{fig:map-physical}}
\end{figure}

@@

\begin{figure}[t!]
\centering
\vspace{-0.3in}
\includegraphics[width=\columnwidth]{paper/figures/results/fits/ions-fitres.png}
\vspace{-0.2in}
\caption{Scatter diagrams (left) and quantile-quantile plots (right) for the hyperparameter optimized RFR models for the ion measurements made by the USV.\label{fig:ions-fit}}
\end{figure}

\begin{figure}[t!]
\begin{adjustwidth}{-\extralength}{0cm}
\centering
\vspace{-0.1in}
\includegraphics[width=18 cm]{paper/figures/results/fits/ions-ranking.pdf}
\vspace{-0.1in}
\end{adjustwidth}
\caption{Ranked permutation importance for the top 25 features of the ion models. The permutation importance measures the decrease in model $R^2$ value when each feature is replaced by a random permutation of its values.\label{fig:ions-fi}}
\end{figure}

\begin{figure}[t!]
\centering
\vspace{-0.3in}
\includegraphics[width=\columnwidth]{paper/figures/results/maps/ions.pdf}
\vspace{-0.2in}
\caption{Maps generated by applying the trained ion models to the data cubes collected on 11-23. Overlaid on the maps are the in-situ reference measurements for the same collection period. The size of the squares has been exaggerated for the visualization. We note that there is good agreement between the generated map and the reference data. \label{fig:map-ions}}
\end{figure}

@@

\begin{figure}[t!]
\centering
\vspace{-0.3in}
\includegraphics[width=\columnwidth]{paper/figures/results/fits/biochemical-fitres.png}
\vspace{-0.2in}
\caption{Scatter plots (left) and quantile-quantile plots (right) for the final hyperparameter optimized models for the biochemical targets blue-green algae (phycoerythrin), CDOM, chlorophyll-a, and blue-green algae (phycocyanin). \label{fig:biochem-fit}}
\end{figure}

\begin{figure}[t!]
\centering
\vspace{-0.3in}
\includegraphics[width=0.9\columnwidth]{paper/figures/results/fits/biochemical-ranking.pdf}
\vspace{-0.15in}
\caption{Ranked permutation importance for each feature in the trained biochemical models. The permutation importance measures the decrease in model $R^2$ value after replacing each feature with a random permutation of its values.\label{fig:biochem-fi}}
\end{figure}

\begin{figure}[b!]
\centering
\vspace{-0.35in}
\includegraphics[width=0.92\columnwidth]{paper/figures/results/maps/biochemical.pdf}
\vspace{-0.15in}
\caption{Maps generated by applying the trained biochemical models to the data cubes collected on 11-23. Overlaid are the in-situ reference data for the same collection period. The size of the squares has been exaggerated for the visualization. We note there is good agreement between the predicted map and the reference data. \label{fig:map-biochem}}
\end{figure}

\begin{figure}[t!]
\centering
\vspace{-0.3in}
\includegraphics[width=\columnwidth]{paper/figures/results/fits/chemical-fitres.png}
\vspace{-0.25in}
\caption{Scatter diagrams (left) and quantile-quantile plots (right) for the hyperparameter optimized RFR models for the chemical variables measured by the USV.\label{fig:chemicals-fit}}
\end{figure}

\begin{figure}[t!]
\centering
\vspace{-0.25in}
\includegraphics[width=\columnwidth]{paper/figures/results/fits/chemical-ranking.pdf}
\vspace{-0.25in}
\caption{Ranked permutation importance for for the top 25 features of the chemical models. The permutation importance measures the deacrease in model $R^2$ value after replacing each feature in the prediction set with a random permutation of its values.\label{fig:chemicals-fi}}
\end{figure}

\begin{figure}
\centering
\vspace{-0.3in}
\includegraphics[width=\columnwidth]{paper/figures/results/maps/chemical.pdf}
\vspace{-0.25in}
\caption{Maps generated by applying the trained chemical variable models to the hyperspectral data cubes collected on 11-23. Overlaid are color-filled squares showing the in-situ reference data for the same collection period. The size of the squares is exaggerated for the visualization. We note that there is good agreement between the model predictions and reference data.\label{fig:map-chem}}
\end{figure}

@@
